%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}

\usepackage{fancyhdr, enumitem}
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Pooja}{Pathak}{ \urlstyle{same}\href{}{} \href{}{}
\href{mailto:poojapathak1725@gmail.com}{poojapathak1725@gmail.com} | (408) 816-3045
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of California, \newline San Diego}
\descript{B.S Cognitive Science, \newline Machine Learning and Neural Computation }
\descript{Minor in Computer Science}
\location{Exp. 2021 | San Diego, CA}
\location{GPA: 3.91}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github: \href{https://github.com/poojapathak1725}{\bf poojapathak1725} \\
LinkedIn:  \href{https://www.linkedin.com/in/pathakpooja/}{\bf pathakpooja} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
Algorithms and System Analysis \\
Advanced Data Structures \\
Computer Architecture \\
Linear Algebra \\
Data Science in Practice \\
Discrete Math \\
Unix and Scripting  \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Skills}
%Embedded Electronics and Systems \\
%Computer Vision \\
%3D Design and Manufacturing \\
%PCB Design \\
%Kernel Programming \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Languages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\vspace{0cm}Technical Skills}

\location{Languages:}
\begin{itemize}[nosep, wide=0pt, leftmargin=*, after=\strut]
\item Python
\item C++
\item Java
\item C
\item Perl
\item HTML
\item Numpy
\end{itemize} 
\location{Frameworks:}
\begin{itemize}[nosep, wide=0pt, leftmargin=*, after=\strut]
\item AWS
\item OpenCV
\item TensorFlow
\item SQLite
\item Linux
\item Git
\end{itemize} 
%\begin{itemize}[nosep, wide=0pt, leftmargin=*, after=\strut]
%\end{itemize} 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Center for Applied Internet Data Analysis}
\descript{ \hspace*{\fill} Research Software Intern }
\location{June 2020 - Present \hspace*{\fill} San Diego Supercomputer Center, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed Python and Perl scripts to analyze raw Internet network traces and present data in programmer desired formats.
\item Parsed large datasets of ASes, relationships, links, paths and prefixes to create new datasets to analyze the growth of IPv4 and IPv6 ASes.
\end{tightemize}
\sectionsep

\runsubsection{EarthSense Inc. }
\descript{ \hspace*{\fill} Software Engineering Intern}
\location{July 2019 – Sep 2019 \hspace*{\fill} Champaign, IL}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Researched Computer Vision and Machine Learning algorithms to recognize key plant traits through an autonomous robot platform.
\item Deployed a Tensorflow ML model on an FRCNN to detect and count corn stands.
\item Improved accuracy of the training model to within 90 \% precision by implementing a grid search algorithm to optimize hyperparameters.
\item Worked on image calibration and radial undistortion using OpenCV.
\item Worked in onsite field research - assisted with LIDAR testing and data collection and labeling.
\end{tightemize}
\sectionsep

\runsubsection{De Anza College }
\descript{ \hspace*{\fill} Teaching Assistant }
\location{April 2018 – April 2019 \hspace*{\fill} Cupertino, CA}
\begin{tightemize}
\item Tutored and assisted students with Data Structures such as Arrays, Linked Lists, Stacks, Queues, Hashtables, Graphs, and Trees  in Java.
\end{tightemize}
\sectionsep

% \runsubsection{Protect Snow Leopards Project}
% \descript{ \hspace*{\fill} Lead Software Intern}
% \location{Apr 2017 – July 2018 \hspace*{\fill} Great Falls, VA}
% \begin{tightemize}
% \item Collaborated with conservationists in the Himalayan region that utilized camera traps as a method of tracking critically endangered Snow Leopards.
% \item Developed a deep learning application to help classify Snow Leopards, from other animals  with an accuracy of 91\%.
% \end{tightemize}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Racial Discrimination by Law Enforcement}
\descript{ \hspace*{\fill} Software Developer }
\location{April 2020 – June 2020 \hspace*{\fill} San Diego, CA}

\begin{tightemize}
\item Analyzed law enforcement data from San Diego County to determine whether an individual's race affects action taken after a police stop.
\item Plotted informative data visualizations using seaborn and matplotlib.
\item Performed chi-square tests of independence between race and action taken for different reasons for police stop.
\item Trained logistic regression models to 86 \% accuracy that predicted that African-Americans were more likely to have action taken against them for traffic violation. 
\end{tightemize}

\sectionsep

\runsubsection{Github Job Listings Filter}
\descript{ \hspace*{\fill} Software Developer }
\location{Jan 2019 – March 2019 \hspace*{\fill} Cupertino, CA}

\begin{tightemize}
\item Developed a Python application for extracting, filtering and viewing job postings on Github in a user-friendly GUI. 
\item Implemented data retrieval with multithreading and multiprocessing.
\end{tightemize}

\sectionsep

%\runsubsection{Wikipedia Popular Names Webscraping}
%\descript{ \hspace*{\fill} Software Developer }
%\location{Jan 2019 – March 2019 \hspace*{\fill} %Cupertino, CA}

%\begin{tightemize}
%\item Parsed and extracted countries and names from the ‘Most Popular Names’ Wikipedia
%webpage using BeautifulSoup and regex.
%\item Cleaned and loaded the data into an SQLite database.
%\item Implement a Tkinter Python GUI to select and display the most popular names for each
%country.
%\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Organizations} 
\runsubsection{Women in CS}
\descript{ \hspace*{\fill} Co-founder }
\location{Feb 2017 – Feb 2018 \hspace*{\fill} De Anza, Cupertino}

\begin{tightemize}
\item As co-founder of the WiCS (Women in CS) at De Anza, I organized and volunteered for the ‘WiE Women in Engineering Conference’ held at SJSU in 2017.
\item Hosted panels inviting FAANG employees to talk about their experiences.
\item Established weekly ‘Common Interview Questions’ discussions within the club.
\end{tightemize}

%\sectionsep

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     PUBLICATIONS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Publications} 
% \renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
% \bibliographystyle{abbrv}
% \bibliography{publications}
% \nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
